Summary of the Iberian Bees Database

### 2024-02-24 Manuscript/Summary/Summary.Rmd
Update summary (Jose check my coments)

ras.counts <- rasterize(datos.laea[, "Accepted_name"], ras,
  field = "Accepted_name", fun = "count"
)
# str(datos.laea)
datos.laea$total <- datos.laea$Male + datos.laea$Female + datos.laea$Worker + datos.laea$Not.specified
ras.counts2 <- rasterize(datos.laea[, "total"], ras,
  field = "total", fun = "sum"
)
ras2 <- raster(datos.laea, resolution = 30000)
ras.richness <- rasterize(datos.laea[, "Accepted_name"], ras2,
  field = "Accepted_name", fun = function(x, ...) {
    length(unique(na.omit(x)))
  }
)
library(vegan)
ras.chao <- rasterize(datos.laea[, "Accepted_name"], ras2,
  field = "Accepted_name", fun = function(x, ...) {
    estimateR(t(as.matrix(x = table(x), nrow = 1, ncol = x)))[2, 1]
  }
) # 2 chao, 4 ACE #TO DO THIS WELL, we need to recover abundances.

>>>>

ras.counts <- rasterize(datos.laea[, "Accepted_name"], ras,
  field = "Accepted_name", fun = "count"
)
# str(datos.laea)
#NACHO is fixing this here, but should be fixed in data cleaning, right!?
datos.laea$Male[is.na(datos.laea$Male)] <- 0
datos.laea$Female <- as.numeric(datos.laea$Female)
datos.laea$Female[is.na(datos.laea$Female)] <- 0
datos.laea$Worker <- as.numeric(datos.laea$Worker)
datos.laea$Worker[is.na(datos.laea$Worker)] <- 0
datos.laea$Not.specified[is.na(datos.laea$Not.specified)] <-
  ifelse(is.na(datos.laea$Worker) == 0 & is.na(datos.laea$Female) == 0 & is.na(datos.laea$Male) == 0, 1, 0)

datos.laea$total <- datos.laea$Male + datos.laea$Female + datos.laea$Worker + datos.laea$Not.specified
ras.counts2 <- rasterize(datos.laea[, "total"], ras,
  field = "total", fun = "sum"
)
ras2 <- raster(datos.laea, resolution = 30000)
ras.richness <- rasterize(datos.laea[, "Accepted_name"], ras2,
  field = "Accepted_name", fun = function(x, ...) {
    length(unique(na.omit(x)))
  }
)
library(vegan)
ras.chao <- rasterize(datos.laea[, "Accepted_name"], ras2,
  field = "Accepted_name", fun = function(x, ...) {
    estimateR(t(as.matrix(x = table(x), nrow = 1, ncol = x)))[2, 1]
  }
) # 2 chao, 4 ACE #TO DO THIS WELL, we need to recover abundances.
